On The Benefits of Magnitude Estimation Relevance Assessments for Information Retrieval Evaluation

### 2016-09-21 response.tex

\documentclass[a4paper]{article}
\usepackage{xcolor}
\usepackage[top=20mm, bottom=20mm, left=20mm, right=20mm]{geometry}

\newcommand{\comment}[1]{\vspace{1em} \textcolor{red}{{#1}} \vspace{1em}}

\begin{document}
\vspace{1em}
\vspace{1em}

\noindent 21 September 2016
\vspace{1em}

\noindent Dear Maarten,
\vspace{1em}

\noindent Please find herein our response to reviewer's comments 
for our paper.

\vspace{1em}

\noindent We thank the reviewers for their constructive feedback and suggestions
for improvements.
Our responses to particular comments are outlined below.
Changes in the manuscript have been highlighted in red font to make
them easy to spot.

\vspace{1em}

\noindent Best Regards,

\vspace{1em}
\noindent Andrew Turpin
\vspace{1em}
\vspace{1em}

\hrule
\vspace{1em}
\vspace{1em}

@@

\comment{We have added Section 6.4 which summarises the section.}

\section{Reviewer 2}

I like the paper and the problem that it addresses: magnitude
estimation for information retrieval and the use of crowd sourcing
for this purpose. The authors claim that their findings are direct
implications for IR evaluation. This is probably true, but I think
the authors can do a better job of articulating them. I recommend
that each result section 5-8 explicitly (1) starts with one of the
four research questions, (2) answers it, (3) explains what the
ramifications of the answers are for IR evaluation.

\comment{
This has been done for Section 6 (RQ2) by adding Section 6.4, 
Section~7 (RQ3) by adding Section~7.4, and
Section~8 (RQ4) by adding the final paragraph.
We feel RQ1 is reasonably covered in Section~5.
}

@@

Section 7 coincides with the old section 5. 
Figs 10, 11, 12 need legends.

\comment {Again, this seems fine on our copies.}

It would be good to explain the differences in absolute
numbers between Table IV in the TOIS submission and Table 2 in the
SIGIR paper. And why these differences do not matter.

\comment {We have added two sentences at the end of the first paragraph in Section~7.2 
explaining the difference. On closer inspection, we also noticed that the new methodology did make a
difference, and have altered the text in the final paragraph of Section~7.3 accordingly.}

@@

Section 8: I am not sure I am happy with the uncertain ending of
this section. What does the disagreement with Kanoulas and Aslam's
earlier work mean for our ``ideal" evaluation setup?

\comment{We have added a summary paragraph to the end of Section~8.1.}

@@

Section 9: the addition of a ``limitations" section is an excellent
idea.

Appendix A: I like this addition. A screen dump of the instruction
interface would have been helpful.

\comment{The exact instructions that appeared on the screen are already
given in the appendix, and a screen dump would just format them in an
HTML/www style, rather than text.
As such, we don't think that an extra screen dump of the instructions
would be informative.
% (In any case, it unfortunately turns out that CrowdFlower has undergone
% an `upgrade' since we ran the experiments, so, sadly, the exact screen
% shot is no longer available anyway.)
}

### 2016-09-28 8_results_RQ4.tex
Submitted post review.
Made all of Maarten's changes (even the footer cite!) except for figure legends. Awaiting email...

Kanoulas and Aslam~\cite{KanAsl03} recommend a ratio of 1.1 for the
gain values of relevant to highly relevant documents to maximize the
effectiveness of a system comparison experiment.
Using magnitudes directly as gain values gives a median of 1.00, 1.00,
and 1.14 in the three boxes in Figure~\ref{fig:ka}, which happens to be
close to their recommendation.
However, again, we see a wide variation from this median, and mean
values of the ratios are 48, 22 and 24 respectively, further suggesting
that there may not be a single gain setting that is suitably
representative across different user perceptions and tasks.
% This hints that using median aggregation might be best for maximizing the statistical efficiency of system
% comparisons using magnitudes as gain values.
% \aht{Really - does this last sentence even make logical senes? median of ratios matches, so use median
% aggregation???}

@@

\subsection{Summary}

>>>>

\citet{KanAsl03} recommend a ratio of 1.1 for the
gain values of relevant to highly relevant documents to maximize the
effectiveness of a system comparison experiment.
Using magnitudes directly as gain values gives a median of 1.00, 1.00,
and 1.14 in the three boxes in Figure~\ref{fig:ka}, which happens to be
close to their recommendation.
However, again, we see a wide variation from this median, and mean
values of the ratios are 48, 22 and 24 respectively, further suggesting
that there may not be a single gain setting that is suitably
representative across different user perceptions and tasks.
% This hints that using median aggregation might be best for maximizing the statistical efficiency of system
% comparisons using magnitudes as gain values.
% \aht{Really - does this last sentence even make logical senes? median of ratios matches, so use median
% aggregation???}

@@

%\subsection{Summary}

### 2016-09-28 ME-TOIS.tex
started making changes!
Attempted to fix the missing answer to RQ2.
Made all of Maarten's changes (even the footer cite!) except for figure legends. Awaiting email...

\begin{bottomstuff}
Author's addresses: Eddy Maddalena, University of Udine, Udine 33100,
Italy, eddy.maddalena@uniud.it; 
Stefano Mizzaro, University of Udine, Udine 33100, Italy,
mizzaro@uniud.it; 
Falk Scholer. RMIT University, Melbourne, Victoria 3001, Australia,
falk.scholer@rmit.edu.au; 
Andrew Turpin, University of Melbourne, Melbourne, Victoria 3010,
Australia, aturpin@unimelb.edu.au. This paper is a revised and
extended version of \citet{ME-SIGIR15}.
\end{bottomstuff}

@@

\input{1_intro.tex}
\input{2_bg.tex}
\input{3_methods.tex}
\input{4_descriptive_stats.tex}
\input{5_results_RQ1.tex}
\input{6_results_RQ2.tex}
\input{7_results_RQ3.tex}
\input{8_results_RQ4.tex}
%\input{9_comments.tex}
\input{10_conc.tex}
\input{11_appendix.tex}

%Acknowledgments
\begin{acks}
  This work was supported in part by the Australian Research Council
  (\emph{Discovery Project} DP130104007) and in part by a Google Faculty Research Award. 
\end{acks}

@@

>>>>

\begin{bottomstuff}
This paper is a revised and
extended version of a SIGIR2015 paper \cite{ME-SIGIR15}.
Author's addresses: Eddy Maddalena, University of Udine, Udine 33100,
Italy, eddy.maddalena@uniud.it; 
Stefano Mizzaro, University of Udine, Udine 33100, Italy,
mizzaro@uniud.it; 
Falk Scholer. RMIT University, Melbourne, Victoria 3001, Australia,
falk.scholer@rmit.edu.au; 
Andrew Turpin, University of Melbourne, Melbourne, Victoria 3010,
Australia, aturpin@unimelb.edu.au. 
\end{bottomstuff}

@@

\input{1_intro.tex}
\input{2_bg.tex}
\input{3_methods.tex}
\input{4_descriptive_stats.tex}
\input{5_results_RQ1.tex}
\input{6_results_RQ2.tex}
\input{7_results_RQ3.tex}
\input{8_results_RQ4.tex}
%\input{9_comments.tex}
\input{10_conc.tex}

%Acknowledgments
\begin{acks}
  This work was supported in part by the Australian Research Council
  (\emph{Discovery Project} DP130104007) and in part by a Google Faculty Research Award. 
  Thanks to both the SIGIR 2015 and TOIS reviewers who 
  helped improve this manuscript.
\end{acks}

@@

\input{11_appendix.tex}
